---
title: "Regression Models Course Project"
author: "Gaurab Kundu"
date: "2022-11-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Executive Summary

Motor Trend, an automobile trend magazine is interested in exploring the relationship between a set of variables and miles per gallon (MPG) outcome. In this project, we will analyze the mtcars dataset from the 1974 Motor Trend US magazine to answer the following questions:

Is an automatic or manual transmission better for miles per gallon (MPG)?

How different is the MPG between automatic and manual transmissions?

Using simple linear regression analysis, we determine that there is a signficant difference between the mean MPG for automatic and manual transmission cars. Manual transmissions achieve a higher value of MPG compared to automatic transmission. This increase is approximately 2.1 MPG when switching from an automatic transmission to a manual one, with the weight, horsepower and discplacement held constant.

# Exploratory Data Analysis

## Loading Required Librarires

```{r}
library(ggplot2)
```

## The Data "mtcars"

```{r}
data(mtcars)
head(mtcars)
str(mtcars)
```

## Transform certain variables into factors

```{r}
mtcars$cyl  <- factor(mtcars$cyl)
mtcars$vs   <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am   <- factor(mtcars$am,labels=c("Automatic","Manual"))
```

To help us understand the data, we build exploratory plots. Appendix - Plot 1, shows there is a definite impact on MPG by transmission with Automatic transmissions having a lower MPG.

# Regression Analysis

